Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-03 neurips-20/cvx-flats.tex
Pass reorganizing thm 2

	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We now claim there is some $u \in \Gamma(p)$ with $\psi(u) = r$.
	First, if $|\gamma(p)| = 1$, then any $u \in \Gamma(p)$ must link to $r$ as we contradict indirect elicitation otherwise; we would have $p \in \Gamma_u$ but $p \not \in \gamma_{\psi(u)}$.
	Now if $\gamma$ is elicitable and $p \in \relint{\simplex}$, we know that $\psi(u) = r'$ for some $r' \in \R$.%suppose there is another $r' \in \R$ with $r \neq r'$ and $r' \in \gamma(p)$.
	If $r' \neq r$, we can show $p \in F \cap \simplex \subseteq \gamma_{r'} (\iff p \in F \cap \simplex \subseteq \gamma_{r})$, where the if and only if comes from Lemma~\ref{lem:set-valued-prop-flats}.
%	Fix $p \in \simplex$ and $r \in \gamma(p)$.
  \jessie{Show that there is some $u \in \Gamma(p)$ such that $\psi(u) = r$.}
	We will show $F \cap \simplex \subseteq \Gamma_u$; the result then follows from $\Gamma_u \subseteq \gamma_r$.
	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
  % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)

	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$.
	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$;
  cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
  To see $F \cap \simplex \subseteq \gamma_r$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u \subseteq \gamma_r$.
\end{proof}

>>>>

	Let $\Gamma := \prop{L}$ and suppose $(L, \psi)$ indirectly elicits $\gamma$, so that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	Since $\Gamma$ is nonempty by assumption, we know there is some $u \in \Gamma(p)$.

	We will first show $F \cap \simplex \subseteq \Gamma_u$; then show $\Gamma_u \subseteq \gamma_r$.
	As $L$ is convex and elicits $\Gamma$, we have $u \in \Gamma(p) \iff \vec 0 \in \partial \exploss{L}{u}{p} \iff \vec 0 \in \oplus_y p_y \partial L(u,y)$, where $\oplus$ denotes the Minkowski sum~\citep[Theorem 4.1.1]{hiriart2012fundamentals}.
  % (Observe that in order for $L$ to be convex, $L(\cdot, y)$ must be convex for all $y \in \Y$.)

	Expanding, we have $\oplus_y p_y \partial L(u,y) = \{ \sum_{y\in\Y} p_y x_y : x_y \in \partial L(u,y) \; \forall y\in\Y\}$.
	Defining the matrix $W = [x_1, \ldots, x_n] \in \reals^{d\times n}$, we have $W p = \sum_y p_y x_y = \vec 0$;
  cf.~\cite[$\mathbf{A}^m$ in Theorem 16]{ramaswamy2016convex}.
	Now taking $F := \ker(W) \cap \affhull(\simplex)$, we have $\codim(F) = \rank(W) \leq d$, and $p \in F$ by construction.
  To see $F \cap \simplex \subseteq \gamma_r$, from the chain of equivalences above, we have for any $q\in\simplex$ that $q \in \ker W \implies u \in \Gamma(q) \implies q \in \Gamma_u \subseteq \gamma_r$.

  %now the justification of r vs r'
  Let $r' = \psi(u)$; we then have $\gamma_{r'}$ containing $F \cap \simplex$.
  If $|\gamma(p)| = 1$, then we are done; otherwise we have $\gamma$ elictable and $p \in \relint{\simplex}$.
  Moreover, if $r = r'$, we are done.
  Otherwise, we can apply Lemma~\ref{lem:set-valued-prop-flats} to observe that $p \in \gamma_r \cap \gamma_{r'}$, and since $p \in F \cap \simplex \subseteq \gamma_{r'} \implies p \in F \cap \simplex \subseteq \gamma_r$.

\end{proof}
